Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-18 Article/ici_submm_cloudcorr.tex
re-organised results, methods section, cleaned text

This information can be used as a pure filter, by rejecting data where the
correction exceeds some threshold value. This threshold value should be
relatively low, to not introduce a bias in filtered dataset. However, even
better is to replace the original value with the predicted NFSC value when
forming the clear-sky dataset. This approach we denote as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature removes the need of threshold value, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach allows that the full weight of
clear-sky data can be preserved.

@@

>>>>

This information can be used as a pure filter, by rejecting data where the
correction exceeds some threshold value. This threshold value should be
relatively low, to not introduce a bias in filtered dataset. However, even
better is to replace the original value with the predicted NFCS value when
forming the clear-sky dataset. This approach we denote as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature removes the need of threshold value, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach allows that the full weight of
clear-sky data can be preserved.

@@

\section{Data and methods}
%
\subsection{Satellite Instruments}
In this section, the different satellite instruments used in this study are described.
\subsubsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels relevant to this study.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	\\
				& [GHz]			& [MHz]			& [K]			\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		\\
		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		\\
		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		\\
		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		\\
		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		\\
		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		\\
		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		\\
		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		\\
		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		\\
		I11V&	664.00$\pm$4.20    & \phantom{0}500	& 1.6 		\\
		I11H&	664.00$\pm$4.20    & \phantom{0}500 & 1.6 		\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	n\\
				& [GHz]			& [MHz]			& [K]			\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2000 			& 1.3 		\\
		MWI-15&	183.31$\pm$6.10    & 1500			& 1.2 		\\
		MWI-16&	183.31$\pm$4.90    & 1500			& 1.2 		\\
		MWI-17&	183.31$\pm$3.40    & 1500			& 1.2 		\\
		MWI-18&	183.31$\pm$2.00    & 1500			& 1.3 		\\	
		\bottomhline
	\end{tabular}

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG(EUMETSAT Polar System - Second Generation) satellite Metop-SG. Metop-SG is scheduled for launch in 2023, and will make ICI the first operational sensor observing Earth using sub-millimeter(sub-mm) wavelengths. ICI is a conically scanning radiometer that will measure 13 frequencies from 183 GHz up to 664 GHz. The main objective of ICI is to use high frequency channels for measuring ice cloud properties and improve the representation of ice clouds in regional and global Numerical Weather Prediction(NWP) models. ICI consists of channels receiving frequencies around 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, measuring vertical polarization. While other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,Km with sensor viewing angle 44.767$^\circ$(measured from nadir). For all the channels, the mean footprint size is about 15\,Km, but the exact geo-location of samples differs. Therefore a simultaneous utilization of data from different channels requires remapping to a common footprint \citep{eriksson:towar:20}.

For this study, we conducted the forward simulations at frequencies: 183.31\,GHz, 325.15\,GHz, 448.00\,GHz and 664.00\,GHz(See Table~\ref{tab:ICI_MWI_channels}). For brevity, we assumed that all simulations were mapped to a common footprint.

\subsubsection{MicroWave Imager}
%
\label{mwi_channels}
In addition to ICI, the Metop-SG will also have Microwave Imager(MWI) on board. MWI is a conically scanning radiometer and will measure frequencies from 18 GHz up to 183\,GHz \todo{add ref}. All channels up to 89 GHz will receive both horizontal and vertical polarisation, while other frequencies will receive only vertical polarisation. A short summary of the MWI channels used in the study is provided in Table~\ref{tab:ICI_MWI_channels}. MWI also has three  183\,GHz frequencies in common with ICI. The overlapping frequencies shall allow cross-calibration between the two instruments, and provide microwave measurements from 18\,GHz to 664\,GHz on a common scale. The main objective of MWI is to provide data continuity to the existing microwave imager measurements for cloud and precipitation and support regional and global NWP models.

For this study, forward simulations at frequencies around 183.31\,GHz were performed. When ICI and MWI simulations were used together, MWI channels were assumed to be mapped to ICI footprint and resolution. Remapping reduces the noise in MWI from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.

\subsubsection{Artic Weather Satellite}
%
\begin{table}[t]
	\caption{Specifications of AWS channels relevant to this study.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		AWS-32	&	176.311    & 2000	&		\\
		AWS-33	&	178.811    & 2000 	&	\\
		AWS-34	&	180.311    & 1000 	&	\\
		AWS-35	&	181.511    & 1000 	&	 \\
		AWS-36	&	182.311    & \phantom{0}500  &	 \\
		AWS-41  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		AWS-42  & 325.15$\pm$4.10    & 1800    &0.75	\\
		AWS-43  & 325.15$\pm$2.40    & 1200    &0.92\\
		AWS-44  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
Earth Watch Programme Element. It is a small platform carrying a single across-track scanning microwave radiometer. It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites. The first prototype mission is expected to be delivered around 2023. The main objective of AWS will be to improve the representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts. AWS will will have channels receiving frequencies around 89.00\,GHz, 165.5\,GHz, 183.31\,GHz, 229.00\,GHz and 325.15\,GHz. For a detailed description of the AWS channels see \citet{eriksson2020study}.

In this study, forward simulations at frequencies 183.31\,GHz and 325.15\,GHz were conducted. A brief summary of these channels is provided in Table~\ref{tab:specifications_AWS}.

\subsubsection{Cloud Profiling Radar}
%
Cloud Profiling Radar(CPR) is the main instrument on sun-synchronous polar orbit satellite CloudSat (Cloud Satellite) \citep{Stephens2002cloudsat}. It was launched in 2006 and is part of the A-train constellation of four earth observation satellites. CPR is a nadir looking radar operating at 94.05\,GHz and measures the cloud backscatter as a function of distance from the radar, to provide vertical profiles of clouds and precipitation.

In this study, CloudSat profiles were used only to perform the forward simulations for ICI, MWI and AWS.

\subsection{Simulations}
\label{sec:arts_simulations}
%
\subsubsection{Input data}
%
Cloudsat profiles during August 2015 were randomly selected for forward simulations. The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land. 
\subsubsection{Simulation setup}
%
**** Some parts copied directly from AWS report *****

\subsubsection{Produced dataset}
%
Using the simulation setup described in previous section,  
220\,000 cases for each ICI and MWI frequency were simulated, using randomly selected CloudSat profiles. For both instruments, the channel frequencies were simulated directly.  
For AWS, 140\,000 cases were simulated. 21 monochromatic frequencies were used and interpolated to a finer grid to get the channel brightness temperatures. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this study are based on nadir viewing angle.

ARTS simulations are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise was added to according to the channel NE$\Delta$T (Table~\ref{tab:ICI_MWI_channels}, Table~\ref{tab:specifications_AWS}). For cases where MWI and ICI simulations were assumed to be remapped to a common footprint, the NE$\Delta$T for corresponding to ICI channels was used (See Sect.~\ref{mwi_channels}).

The noise free simulations were divided into training and testing datasets. Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set. The rest were used for testing. A smaller database was selected for AWS. 120\,000 simulations were used for training and the 
remaining were used for testing.

\subsection{QRNN}
%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimise the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).

\subsubsection{Theory}

\subsubsection{QRNN implementation}
\label{sec:qrnn-implementation}

The implementation of QRNN is based on PyTorch, an open source machine learning library \citep{paszke2017automatic}. It is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}].

For this study, we initialize the quantile loss function with quantile fractions $\tau$ = [0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998] to train the neural network to predict the corresponding quantiles $x_{\tau}$ = [$-3\sigma, -2\sigma, -1\sigma, median, 1\sigma, 2\sigma, 3\sigma $]. QRNN is trained with simulated brightness temperatures from different channels, no other data is included. The input channels are variable and are determined by the type of QRNN model used. The different QRNN models are described in Sect.~\ref{QRNN_models}.

A custom data augmentation scheme is implemented to build a robust learning network. At each training iteration, noise is added to the noise-free inputs according to the measurement uncertainty. The target training data is always kept noise free. This ensures that the model is exposed to different datasets during the entire training process, and avoids memorisation of training samples. The input data is normalized with mean and standard deviation. While training, 10\% of the training data is used for validation.

The neural network is trained with an adaptive form of stochastic batch gradient descent. During the training process, at each iteration, the loss in the validation dataset in monitored. If the validation loss remains stagnant for a certain number of epochs, the training rate is reduced  by a given reduction factor. This process is continued till a minimum learning rate is achieved.

A high performing QRNN model also requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-parameter tuning. In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed. The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc. We use quantile loss and CRPS for evaluation of the model performance.

\subsubsection{ QRNN model configurations}
%
\label{QRNN_models}

\begin{table*}[t]
	\caption{Summary of the different QRNN models used in the study.}
	\label{tab:QRNN_models}
	\begin{tabular}{lllll}
		\tophline
		QRNN model & Instrument & Target & Input 183\,GHz channel(s) &Other training inputs \\
		\middlehline
		QRNN-single &  ICI 	& I1V/I2V/I3V 	& I1V/I2V/I3V, & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{2-5}
		&  MWI 	& MWI-15/MWI-16 & MWI-15/MWI-16	& I5V, I6V, I7V, I8V, I9V, I10V, I11V \\
		\cline{2-5}
		& AWS	& AWS-32/AWS-33/ &  AWS-32/AWS-33/ & AWS-41, AWS-42, AWS-43, AWS-44\\
		&		& AWS-34/		 &	AWS-34/		   & \\
		&		& AWS-35/AWS-36	 & AWS-35/AWS-36,  &\\
		\cline{1-5}
		QRNN-all &  ICI 	& I1V/I2V/I3V 	& I1V, I2V, I3V & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{1-5}
		QRNN-mwi &  MWI		& MWI-14/MWI-15/ &  MWI-14, MWI-15, & None 	\\	
		&			& MWI-16/		 &  MWI-16, & \\
		&			& MWI-17/MWI-18	 &  MWI-17, MWI-18  &\\					
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

In the study, three types of QRNN models are formulated. For each type, the target is always one of the available 183\,GHz channels, and this target channel is always included in the training set. The choice of other channels in the training set depends on the type of QRNN model chosen. A summary of the three QRNN models described in this study is provided in Table~\ref{tab:QRNN_models}.

In the first model, ``QRNN-single'', the training inputs always contain data from the target 183\,GHz channel, and one or more available sub-mm channels. Other 183\,GHz channels are not included in the training. For ICI and MWI, 325\,GHz, 448\,GHz and 664\,GHz channels are used in the training, while for AWS only 325\,GHz is used.

The second model, ``QRNN-all'', is defined to investigate the  impact of using all 183\,GHz channels concurrently. In this model, the training set includes data from all available 183\,GHz channels, along with other sub-mm channels. This model is applied only to ICI. It should be noted that although the training set is identical for I1V, I2V and I3V, a separate training is needed for each channel as target.

The third model, ``QRNN-mwi'' is used only for MWI channels. In this case, all 183\,GHz channels are used concurrently in the training set. No other data from sub-mm channels is used.

\section{Results}
%
In this section, QRNN is used to predict the NFCS values for operational humidity channels. The main aim of this study is to demonstrate that sub-mm channels can be used to formulate the cloud filtering/correction of data measured around 183\,GHz. Different combinations of 183\,GHz channels and sub-mm channels are applied to QRNN and the results are compared. The impact of different hyper-parameters on QRNN performance is also discussed. NFCS simulations are used to analyse the prediction accuracy. Results from both pure-filtering and correction are described. Furthermore, the case specific uncertainties obtained from QRNN are also discussed.

\subsection{QRNN network structure}
%
\begin{figure*}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) averaged over all predicted quantiles for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-single applied to I2V.}
	\label{fig:grid_search}	
\end{figure*}
In this study, we investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size. The optimization of other hyper-parameters was not performed and were chosen empirically. Firstly, we performed a grid search to define the structure of the neural network. We evaluated the performance for three sizes of hiddden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512]. The mean quantile loss and CRPS over all predicted quantiles was computed for each configuration (Fig.~\ref{fig:grid_search}). Increasing the complexity of the network by increasing the layer width and depth has a positive impact on performance. However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance. On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected. For optimising the training parameters, a customised  learning rate scheduler was implemented. The initial learning rate was reset after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times with a new initial learning rate. For each training, if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2. 
In order to select the batch size, we simply compared the performance for for two batch sizes: 128 and 256, and the former gave better results. Concerning number of epochs, we obtained best results when the network was trained longer. Choosing a lower value of epochs (e.g. 50), did not affect the accuracy of the median value, yet deteriorated the prediction uncertainty. We did not optimise the type of activation function and Rectified Linear Unit (ReLu) was used in all layers.

Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other channnels and other QRNN models as well. All the results described in this study used an identical hyper-parameter configuration.

\subsection{ICI}
\subsubsection{Example results}
%
%f
\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
	\caption{Posterior distribution obtained from QRNN-single (I2V) for three different cases. }
	\label{fig:posterior_distribution_I2V}	
\end{figure}
%f
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of point estimate NFCS from QRNN-single for channels I1V, I2V and I3V. The corresponding distributions for NFCS simulations are also shown.}
	\label{fig:PDF_predictions}	
\end{figure*}
QRNN predictions are estimates of the posterior distribution over different quantiles. For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ (Sect.~\ref{sec:qrnn-implementation}). The quantiles are interpreted as probabilistic predictions and can be used to construct a probability distribution of the predictions. Fig.~\ref{fig:posterior_distribution_I2V} exemplifies the posterior distribution predicted by QRNN-single. The three cases shown in the figure have a similar median value but very different spread. The spread of the distributions can also be expressed as the prediction interval. If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval. It is gives the range where the prediction could be located and its length is a measure of the reliability. Among the three cases shown in the figure, the blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability. While the other two cases have longer intervals implying higher fluctuations, or low reliability. The quantiles can also be used to interpret the confidence intervals. For a given case, if two quantiles $\tau_1$ and $\tau_2$ are chosen, then there is $\tau_2 - \tau_1$ chance that the true value ($y_o$) shall lie in in range $[y_{\tau_1}, y_{\tau_2}]$. For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_2 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$. More on confidence interval is discussed in Sect.~\ref{sec:prediction_uncertainty}.

For an analysis of QRNN predictions, a point estimate of the posterior distribution is required. Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value. The distribution of point estimates is shown in Fig.~\ref{fig:PDF_predictions}. For clear-sky conditions, I1V has the warmest brightness temperatures and I3V has the coldest. For all three channels, an excellent agreement between the predictions and simulations is observed, indicating that QRNN is successful in predicting NFCS values for majority of the cases. At lower brightness temperatures, the frequency of predictions is slightly smaller than simulations. This could be due to few QRNN predictions ending up with partially corrected cloud impact.

\subsubsection{Analysis of cloud filtering}
%
\label{sec:cloud_filtering}
%f 
\begin{figure*}[t ]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Error distributions for deviations of filtered and predicted data to clear-sky simulations. The results are from QRNN-single and channels I1V, I2V and I3V. Noise for each channel is also plotted for reference. The label ``Uncorrected'' represents the measurement data and ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are rejected. ``Predicted(All)'' denotes the entire prediction dataset, while ``Predicted(5\,K)'' refers to the predicted dataset but where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distributions}	
\end{figure*}
\begin{table*}[t]
	\caption{ Error statistics for deviations of filtered and predicted data to NFCS simulations. 
		The values for Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) are shown. Results are from both QRNN-single and QRNN-all for channels I1V, I2V and I3V. The number in parentheses is the percentage of cases removed by filtering. The label ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are rejected, ``Predicted(All)'' refers to the complete predicted dataset, while ``Predicted (5\,K)'' denotes the prediction dataset but where cases with cloud correction greater than 5\,K are excluded.}
	\label{tab:error_statistics_ici}
	%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-single} & \multicolumn{3}{c}{QRNN-all}\\
		\cline{3-10}
		%		\hline
		&&   Clear-sky &   All-sky &  Filtered & Predicted & Predicted &   Filtered & Predicted & Predicted \\
		&&&&							(5\,K) &(All)& (5\,K) & (5\,K)&(All)& (5\,K)\\
		\middlehline
		%		\multicolumn{7}{c}{Channel - I1V}\\

		I1V& Bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
		&MAE      &  0.64 &  2.32 &  0.79 &  0.64 &  0.55 &  0.78 &  0.61 &  0.54 \\
		&STD      &  0.80 &  8.84 &  1.07 &  0.98 &  0.73 &  1.07 &  0.91 &  0.71 \\
		&Skewness & -0.01 & -8.10 & -1.53 & -1.53 & -0.75 & -1.52 & -1.07 & -0.55 \\
		\middlehline
		I2V &Bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
		&MAE      &  0.64 &   1.52 &  0.74 &  0.52 &  0.46 &  0.75 &  0.44 &  0.39 \\
		&STD      &  0.80 &   5.95 &  0.99 &  0.82 &  0.59 &  0.99 &  0.67 &  0.50 \\
		&Skewness &  0.00 & -10.80 & -1.10 & -2.17 & -0.27 & -1.05 & -2.22 & -0.27 \\
		\middlehline	
		I3V &Bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
		&MAE      &  0.64 &   1.15 &  0.71 &  0.51 &  0.47 &  0.72 &  0.46 &  0.42 \\
		&STD      &  0.80 &   4.27 &  0.93 &  0.77 &  0.59 &  0.95 &  0.68 &  0.54 \\
		&skewness & -0.00 & -13.41 & -0.86 & -1.75 & -0.11 & -0.93 & -1.53 & -0.14 \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

In this section, we use the point estimates to formulate a cloud filtering scheme. All cases with  cloud correction greater than a certain threshold are classified as cloudy and omitted from the dataset. Cloud correction is calculated as the difference of the point estimate and the corresponding measurement. Since this is a pure-filter, for the cases classified as clear-sky, the a priori values are used instead of the point estimates.

To implement the cloud filtering scheme, we chose 5\,K cloud correction as the filtering threshold. All cases with correction greater than 5\,K were rejected. In order to analyse the performance of the filtering threshold, the deviations of the filtered measurements to the simulated NFCS values were calculated. Fig.~\ref{fig:error_distributions} shows the distribution of the deviations for filtered(red) and original datasets(green). Cloud contamination causes a reduction in the brightness temperatures, and introduces a large negative bias in the error distributions. Without any cloud impact, the error distributions must follow a Gaussian distribution with a narrow spread. When filtering is activated, and all cases with correction greater than 5\,K are rejected, the resulting distributions have a low but asymmetric spread. The right side of the distributions follows measurement noise, as expected, and the left side has a significantly smaller negative skewness than the measurements. This indicates that 5\,K filter can successfully remove cases associated with high cloud impact. However at the same time, the asymmetric error distribution indicates that cases with low cloud impact are erroneously classified as clear-sky.

For a quantitative assessment of the performance achieved with cloud filtering, we calculated the average error bias, MAE (mean absolute error) and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness: 
\begin{equation}
g_1 = \frac{m_3}{m_2^{3/2}}, 
\end{equation}
where $m_2$ and $m_3$ are biased sample's second and third central moments. The error metrics corresponding to the error distributions described in Fig.~\ref{fig:error_distributions} are provided in Table~\ref{tab:error_statistics_ici} under label "Filtered(5\,K)". The average bias in I1V measurements is -1.88\,K, and rejecting around 6\% of the cases as cloudy reduces the bias to -0.32\,K. The standard deviation also reduces to 1.07\,K from 8.84\,K. Similarly for I2V, the average error bias in all sky measurements is -1.04\,K, that reduces to -0.24\,K after filtering. The corresponding improvement in MAE was almost 65\%. Only 3.7\% of the total cases were rejected to achieve this accuracy. For I3V, filtering classifies 2.3\% of the total cases as cloudy and reduces the bias to 0.18\,K from -0.63\,K and the standard deviation from 5.95\,K to 0.91\,K. The results from QRNN-all are also shown in the same table. Using all 183\,GHz channels concurrently has no notable impact on the cloud filtering. Almost similar statistics are obtained from QRNN-single and QRNN-all. Overall for all three channels, the notable decrease in the errors indicates that the cloud filter is effective in removing most of the cloudy cases, however few cases with low cloud impact still pass through the filter and deteriorate the performance. This indicates that though a pure-filtering approach can prove as a reliable procedure for removing cases with high cloud impact, additional measures are needed to remove cases with low cloud impact.

A lower filtering threshold can help alleviate this problem to certain extent, however that can come at the cost of high rejection rate. We investigated the performance of cloud filtering with different threshold values. Fig.~\ref{fig:filtering_thresholds} shows the average errors obtained from different filtering thresholds and the corresponding percentage of data omitted. Lowering the filtering threshold from 5\,K to 2.5\,K has only a small effect on the filter performance. However, a further decrease in the filtering threshold decreases the average error bias significantly, albeit with a high rejection rate. For example, for I1V, when all cases with cloud correction greater 0.5\,K are filtered, the mean error bias of the subset is -0.06\,K, MAE is 0.59\,K and the standard deviation is 0.75\,K. Though, these values are comparable to the NFCS simulations, the high performance comes at the cost of rejecting more than 30\% of the total cases. The high fraction of rejection is a consequence of clear-sky cases being erroneously classified as cloudy. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy.

\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
	\caption{A comparison of the  average bias when pure-filtering approach (QRNN-single) is applied with different thresholds (red curves). The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).}
	\label{fig:filtering_thresholds}	
\end{figure}

\subsubsection{Error of best estimate}  
%
%t
\begin{table*}[t]
	\caption{A comparison of the error statistics from QRNN-single and QRNN-all, when only cases with cloud correction greater than 10\,K are included. The number in the parentheses gives the fraction of cases included.}
	\label{tab:error_statistics_ici_high_cloud_impact}
	%	\tabcolsep=0.11cm
	\begin{tabular}{lrr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{I1V}& \multicolumn{2}{c|}{I2V} & \multicolumn{2}{c}{I3V}\\
		\cline{2-7}
		&QRNN-single& QRNN-all & QRNN-single & QRNN-all  & QRNN-single & QRNN-all\\
		\middlehline
		Bias     & -0.53(4.02\%) & -0.38(4.07\%)  & -0.42(2.26\%) & -0.46(2.25\%) & -0.25(1.32\%) & -0.40(1.28\%) \\
		MAE      &  2.32 &  1.93  &  2.77 &  2.08 &  3.10 &  2.59 \\
		STD      &  3.13 &  2.63  &  3.65 &  2.85 &  4.03 &  3.47 \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

The QRNN prediction accuracy is estimated by computing the deviation of the best estimate to its corresponding NFCS value (Fig.~\ref{fig:error_distributions}). The predicted values have a symmetric distributions albeit with a large spread. The large spread on the left is due to cases which end up with incomplete cloud correction, while spread on the right is from cases where the predicted values are warmer than the simulations. For all three channels, quite similar behaviour is observed, though I1V has the most cases with residual cloud impact. If the predicted cases with correction more than 5\,K are rejected, the resulting error distributions fit the measurement noise, except for I1V, where cases with residual cloud impact introduces a negative bias.

For a quantitative assessment of the errors, we calculated the error metrics described in Sect.~\ref{sec:cloud_filtering} and the results are displayed in Table~\ref{tab:error_statistics_ici}. The average bias in I1V measurements is -1.88\,K, which reduces to -0.06\,K after cloud correction. The corresponding standard deviation is 0.98\,K in comparison to 8.84\,K in the measurements. The prediction accuracy of QRNN is further higher when filtering is made on the predictions. In this case, the residual bias is only -0.04\,K, and the standard deviation is 0.73\,K, which is in fact of the order of measurement noise (0.80\,K). Similar results are seen for I2V, though a better performance of QRNN is observed. In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction. The MAE reduces from 1.52\,K to 0.52\,K. Removing cases with correction greater than 5\,K from the predictions removes 3.7\% of the data and reduces the absolute error to 0.46\,K and the bias to 0\,K. The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise. The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of the predicted distributions is sharper. In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact. In the predicted dataset, the bias is 0.01\,K and the MAE is 0.51\,K in comparison to 1.15\,K  in the measurements. Including correction along with filtering reduces the MAE further down to 0.47\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).

Next, we describe the results from QRNN-all. In this model, all 183\,GHz channels along with other sub-mm channels are included while training. This model is designed to identify if other channels of the same frequency can provide auxiliary information in the training process. The results from QRNN-all all are provided in the last columns of Table~\ref{tab:error_statistics_ici}. For I1V, using additional information from other two 183\,GHz channels has only a slight positive impact on the predictions. In the prediction dataset, the average bias for QRNN-all and QRNN-single is identical, but the MAE in QRNN-all are almost 4.5\% less than QRNN-single. However when the predictions are filtered with 5\,K threshold, the performance of both models is quite similar. This indicates that information from other channels only assists in slightly improving the correctness of cases associated with high cloud impact in I1V. The predictions of cases with low cloud impact have no significant gain. For I2V, the predictions from QRNN-all have a slightly worse average error bias than QRNN-single, yet a significant improvement in the prediction accuracy is observed. When all predictions are considered, the MAE is 0.44\,K in comparison to 0.52\,K from QRNN-single, showing an improvement of almost 15\%. Similarly the standard deviation of the errors is only 0.67\,K, which is notably smaller than the measurement noise. Additionally, when the predicted dataset is filtered with 5\,K threshold, the accuracy is even better. The mean absolute bias reduces to 0.39\,K and standard deviation to 0.50\,K. This implies that cases pertaining to clear-sky conditions and relatively low/no cloud impact benefit the most from the auxiliary information. This is in contrast to I1V, where accuracy of such cases remained unaffected. For I3V, the performance of QRNN-all is comparable to that for I2V. For I3V, the MAE in QRNN-all is 0.46\,K compared to 0.51\,K from QRNN-single, and the corresponding standard deviations are 0.68\,K and 0.77\,K. Removing the cases with cloud impact greater than 5\,K from the predictions, leads to no change in the average bias, but the MAE and standard deviation reduce by almost  8\% and 20\% respectively. This is again a consequence of improved prediction accuracy of cases with low/no cloud impact.

In order to quantify the positive effect of QRNN-all on cases with high cloud impact, the error statistics for all cases with cloud correction greater than 10\,K were computed (Table~\ref{tab:error_statistics_ici_high_cloud_impact}). For I1V, only 4\% of the cases have cloud correction greater than 10\,K, but very high prediction errors. QRNN-all improves the overall error bias from -0.53\,K to -0.38\,K and the standard deviation from 3.13\% to 2.63\%, but is unsuccessful in removing the cloud impact completely. A likewise improvement is also observed for I2V. Despite both models being only partially successful in removing the cloud impact, QRNN-all has a better performance among the two. For I2V, such cases form only 2.25\% of the testing dataset. Predictions from QRNN-all have slightly worse values for average error bias, but both MAE and standard deviation improve by over 20\%. For I3V also, the cases with high cloud impact, though very low in number, also gained positively from the auxiliary information.

The results show that both QRNN-single and QRNN-all are successful in predicting NFCS values for I2V, and I2V, and partially successful for I1V. The resulting error distributions are symmetric with low bias and standard deviation. For I2V and I3V, the variability of errors is even smaller than the noise. This is a consequence of predictions for cases associated with clear sky conditions. QRNN predictions are weighted mean of measurements between channels. For clear-sky conditions, the averaging of cases observed by multiple channels can cancel out the noise. The cancelling of noise is stronger in QRNN-all as all 183\,GHz channels are used concurrently. The lower prediction accuracy of I1V can be explained by the fact that it is the outermost 183\,GHz channel and the other sub-mm channels cannot provide a full coverage for the hydrometeor impact in I1V. Depending upon the atmospheric scenarios, there is always a portion of data detected by I1V, but never seen by any other channel. Though such cases are few, QRNN cannot learn to predict the clear-sky values accurately for cases which lie outside the coverage area. Besides this, lower representation of high cloud impact cases in the training set also affects QRNN accuracy.
